---
title: Template title
subtitle: Template subtitle
format:
  dopCIP-typst:
    table-of-contents: false
    show-cover: false
    # Set to true to show the title in a band at the top of the first page
    show-title-band: true
    # Set to true to show the city logo in the title band
    title-band-logo: true
    # Scale logo heights (e.g. 0.75 if a long title overlaps the cover logos)
    logo-scale: 1
    # Running header and footer: title, heading-1, heading-2, page-number, or
    # none for each side (defaults shown)
    page-header:
      left: heading-2
      right: none
    page-footer:
      left: heading-1
      right: page-number
    # Page number format, or false to hide page numbers
    page-numbering: "1"
---

# Level 1 heading

{{< dop-toc title="In this section" >}}

## Level 2 heading

{{< lipsum 1 >}}

You can learn more about creating custom Typst templates here:

<https://quarto.org/docs/prerelease/1.4/typst.html#custom-formats>

## Second Level 2 heading

```{r}
#| label: fig-example
#| fig-cap: Example figure caption
#| echo: false
plot(mtcars)
```

```{r}
#| label: tbl-example
#| tbl-cap: Example table caption
#| echo: false

if (rlang::is_installed("gt")) {
  gt::gt(mtcars)
}
```

Example of a definition list:

Term
: Definition

Second Term
: Second Definition

### Level 3 heading

{{< lipsum 1 >}}

# Level 1 heading for tag text examples

Example of "tag text" with no title: [Text inside tag]{.dop-tag-text}

Example of "tag text" with title: [Text inside tag]{.dop-tag-text title="Title of tag"}

Example of "tag text" followed by punctuation: [Text inside tag]{.dop-tag-text}, then a comma and a [second tag]{.dop-tag-text title="Title"}.

Example of "tag text" with an empty title: [Text inside tag]{.dop-tag-text title=""}

Example of adjacent "tag text": [First tag]{.dop-tag-text} [Second tag]{.dop-tag-text}

Example of "tag text" followed by brackets: [Text inside tag]{.dop-tag-text}(in parentheses) and [Text inside tag]{.dop-tag-text}[in brackets]

Example of "tag text" with special characters: [Issue #12 costs $5 and [x] me@x.org **bold**]{.dop-tag-text title='Say "hi" #set'}

Example of long "tag text" with title: [This is a long tagged span of text that needs to wrap across the end of the line to check how the outset looks next to the lines above and below]{.dop-tag-text title="Long"}

# Level 1 heading for table label examples

Example of a table label: [Table label text]{.dop-table-label}

[Table label on its own line]{.dop-table-label}

Example of a table label with special characters: [Issue #12 costs $5 and [x] me@x.org **bold**]{.dop-table-label}, then more text.

{{< pagebreak >}}

[Project details]{.dop-secondary-header}

## Page with a secondary header

The secondary header is placed below the running header line, above the title of this page.

{{< lipsum 1 >}}

{{< pagebreak >}}

[Issue #12 costs $5 & [x] **bold**]{.dop-secondary-header dy="-12pt"}

## Page with a secondary header and a custom offset

The secondary header on this page uses `dy="-12pt"` and includes special characters.

{{< pagebreak >}}

## Page with an invalid secondary header offset

Text before the secondary header in the same section. [Invalid offset]{.dop-secondary-header dy="up"}

The secondary header on this page is placed partway down the page but floats to the top; the invalid `dy` value is ignored with a warning.
