---
title: Untitled
format:
  dopCIP-typst:
    table-of-contents: true
---

# Level 1 heading

## Level 2 heading

{{< lipsum 1 >}}

You can learn more about creating custom Typst templates here:

<https://quarto.org/docs/prerelease/1.4/typst.html#custom-formats>

## Second Level 2 heading

```{r}
#| label: fig-example
#| fig-cap: Example figure caption
#| echo: false
plot(mtcars)
```

```{r}
#| label: tbl-example
#| tbl-cap: Example table caption
#| echo: false

if (rlang::is_installed("gt")) {
  gt::gt(mtcars)
}
```

Example of a definition list:

Term
: Definition

Second Term
: Second Definition


Example of "tag text" with no title: [Text inside tag]{.tag-text}

Example of "tag text" with title: [Text inside tag]{.tag-text title="Title of tag"}

Example of "tag text" followed by punctuation: [Text inside tag]{.tag-text}, then a comma and a [second tag]{.tag-text title="Title"}.

Example of "tag text" with an empty title: [Text inside tag]{.tag-text title=""}

Example of adjacent "tag text": [First tag]{.tag-text}[Second tag]{.tag-text}

Example of "tag text" with special characters: [Issue #12 costs $5 and [x] me@x.org **bold**]{.tag-text title='Say "hi" #set'}

Example of long "tag text" with title: [This is a long tagged span of text that needs to wrap across the end of the line to check how the outset looks next to the lines above and below]{.tag-text title="Long"}


### Level 3 heading

{{< lipsum 1 >}}
